Trill: Secure firewall-traversing networking

### 2012-11-12 6.858/proposal/proposal.tex
Security!

\section*{Security}
% TODO

>>>>

\section*{Security}
The security of our system will be based on standard cryptographic
infrastructure and libraries. By ``identities,'' we mean public key pairs, the
private half of which is uniquely known by an individual. This identity can be
given one or more names by means of X.509 certificates, and standard mechanisms
like TLS allow owners of names to securely establish a communication channel and
mutually verify the other's identity. Due to implementation restrictions in our
target environment, we will be using DTLS, a younger protocol that uses UDP as
its transport layer, and we will be using the implementation of DTLS provided by
the open source GnuTLS library.
